### 2011-03-16 qualificacao/dissertacao.tex
primeira traducao livre do abstract

% ---------------------------------------------------------------------------- %
% Agradecimentos
% TODO: agradecimentos
\chapter*{Agradecimentos}
Agradecimentos ...

% ---------------------------------------------------------------------------- %
% Resumo
\chapter*{Resumo}

@@

% ---------------------------------------------------------------------------- %
% Abstract
% TODO: abstract
\chapter*{Abstract}

\noindent \textbf{Keywords:} Test-Driven Development, Sistemas Orientados
a Objetos, Design de Classes, Métodos Qualitativos de Pesquisa.

@@

		 ISP		 & Princípio da Segregação de Interfaces (\emph{Interface Segregation
		 Principle})
\end{tabular}

@@

\singlespacing              % espaçamento simples
%\onehalfspacing            % espaçamento um e meio

>>>>

% ---------------------------------------------------------------------------- %
% TODO: agradecimentos
\chapter*{Agradecimentos}
Agradecimentos ...

% ---------------------------------------------------------------------------- %
\chapter*{Resumo}

@@

% ---------------------------------------------------------------------------- %
\chapter*{Abstract}

Test-Driven Development (TDD) is one of the most popular practices of Extreme
Programming (XP), and its popularity has grown increasingly among the
developers. The mechanical is simple: the developer should write a test before
writing the implementation. Although TDD may look like a testing practice
(after all, TDD has the word ``test'' in its name), its main contribution is the
feedback in the class design. Most well-known authors claim that TDD, besides
driving the design, it still helps programmers to maintain the code cleaner,
more focused, etc.

It is really hard to understand how TDD influences on the software development
process. And, contrary to what is expected, most part of the experiments in
academia evaluate the effects of TDD in the external quality. As already noticed
by different authors, only a few studies evaluate its effect on internal
quality.

This work aims to understand better the effects and how TDD influences on the
object-oriented systems design, observing the point of view from developers who
practice it. In order to achieve this goal, this research proposes a set of
interviews with brazilian industry developers that practice TDD in their daily
work. In adition, this research makes a comparison of the findings with what is
currenlty found in literature.

\noindent \textbf{Keywords:} Test-Driven Development, Object-Oriented
Systems, Class Design, Qualitative Research Methods.

@@

		 ISP		 & Princípio da Segregação de Interfaces (\emph{Interface Segregation
		 Principle})\\

		 OO		 	 & Orientação a Objetos

\end{tabular}

@@

%\singlespacing              % espaçamento simples
\onehalfspacing            % espaçamento um e meio
